The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2012-06-05 smurf_paper.tex
add in final m17 plots + some of the text for noise/transfer function

While the reduction in the bottom panels of Fig.~\ref{fig:m17} is
clearly superior in at least a cosmetic sense to those in the top
panels, it is important to quantify both the noise properties of the
maps and their response to real structures (the transfer
function). Similar to the previous section, we will use a jackknife
test to estimate the noise, and then inject known sources into the
data to observe how they are attenuated.

Maps are produced using the first and second continuous halves of the
data. This is not an ideal situation since the noise properties may
evolve with time (e.g., due to changing sky conditions) leading to a
biased estimate of the parent noise distribution from the
jackknife. Also, since the zero-masking depends on the SNR of the map,
it will be restricted to regions approximately $\sqrt{2}$ shallower in
these maps than for the full data set. Ideally one would have many
full maps as in the case of the Lockman Hole data in the previous
section, from which alternating maps could be combined. However, for
the discussion at hand our method

@@

Next, we inject simulated clouds into a relative empty portion of the
observation 11 M17 map. It is created by filtering white noise first
with a power-law index $alpha=$bla (a reasonable approximation for
Galactic Cirrus... cite bla bla), and then with a 14.5\,arcsec
Gaussian to model the effect of the SCUBA-2 optical response. Finally,
the signal is apodized ... Compare power-spectrum before and after.

>>>>

\begin{figure*}
\centering
\includegraphics[width=0.8\linewidth]{m17_jk.pdf}
\caption{Maps of M17 used to characterize the noise properties and
transfer function of SMURF. For each column, a different high-pass
filter edge scale was adopted (indicated in the top panels). First
(top) row: Average of two halves of the data analyzed independently,
using the default configuration. The data have had added to them
synthetic signal within a 600\,arcsec diameter circle (S.E. of M17)
created as a realization of noise from a $P(k) \propto k^{-3}$ angular
power spectrum multiplied by the PSF, subtracting the minimum to make
it positive, scaling it to a similar signal range as M17 itself, and
rolling-off the edges smoothly using half a period of a radial
(1+cosine)/2 function across 100\,arcsec beyond the edge of the
600\,arcsec region. Second row: jackknife maps produced from the
differences of the maps of each half of the data that went into the
first row. Third row: average of the two halves of the data using the
bright extended reduction. The blue and red contours indicated the
zero-masked regions in each case (note for the 300\,arcsec case that
the region about M17 matches fairly closely the mask in
Fig.~\ref{fig:m17}d). Clearly as the filter scale is increased, due to
the high SNR of the data, larger emissions regions are (correctly)
detected and reproduced in the map. Fourth (bottom) row: Jackknife
maps for the bright extended reductions.}
\label{fig:m17_jk}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{pspec_m17_default.pdf}
\includegraphics[width=0.49\linewidth]{cor_pspec_m17_default.pdf}
\caption{Angular power spectral densities (PSDs) for the region of the
M17 map in Fig.~\ref{fig:m17_jk} containing synthetic data, using the
default configuration. left: raw PSDs for the input (noiseless)
simulated data (thick black line), the signal (average of each half)
PSDs (thin solid lines), and noise PSDs estimated from the jackknives
(dashed lines). Vertical dotted lines indicate the high-pass filter
scales. The red, green, and blue colours indicate data filtered at
150, 300, and 600\,arcsec scales. right: corrected PSDs. Since the
input PSD is known, it is possible to measure the transfer function of
the map-maker as the ratio between the output map signal and input
PSDs (thick solid lines). The remaining lines are as in the left
panel, but now corrected by the transfer function. This plot shows
that while increasing the filter scale improves the SNR at large
scales ($\gsim100$\,arcsec), it also reduces the SNR at smaller scales
($\lsim100$\,arcsec).}
\label{fig:m17_def_ps}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=0.49\linewidth]{pspec_m17_bright_extended.pdf}
\includegraphics[width=0.49\linewidth]{cor_pspec_m17_bright_extended.pdf}
\caption{Lines have same meaning as in Fig.~\ref{fig:m17_def_ps},
except now using the bright extended configuration. This configuration
has resulted in an improved transfer function and SNR at large angular
scales. Also note that increasing the filter scale does not have as
large of an impact on the small-scale noise as in the default
configuration.}
\label{fig:m17_bc_ps}
\end{figure*}

While the reduction in the bottom panels of Fig.~\ref{fig:m17} is
clearly superior in at least a cosmetic sense to those in the top
panels, it is important to quantify both the noise properties of the
maps and their response to real structures (the transfer function). We
would also like to know these are affected by our choice of filter
scale.  Similar to the previous section, we will use a jackknife test
to estimate the noise, and then inject known sources into the data to
observe how they are attenuated.

Maps are produced using the first and second continuous halves of the
data in Fig.~\ref{fig:m17_jk}. This is not an ideal situation since
the noise properties may evolve with time (e.g., due to changing sky
conditions) leading to a biased estimate of the parent noise
distribution from the jackknife. Also, since the zero-masking depends
on the SNR of the map, it will be restricted to regions approximately
$\sqrt{2}$ shallower in these maps than for the full data
set. Finally, the cross-linking (positional angles sampled) is
similar, though not identical in the two halves. Ideally one would
have many full maps as in the case of the Lockman Hole data in the
previous section, from which alternating maps could be combined.

@@

In addition to dividing the data into two halves, we also inject
simulated clouds into a relative empty portion of the map. It is
created by drawing a realization of noise within an 800\,arcsec
on-a-side box, from an angular power spectrum $P(k) \propto k^{-3}$
which is appropriate for Galactic cirrus clouds
\citep[e.g.][]{gautier1992}. It is then filtered again with a
14.5\,arcsec Gaussian to model the effect of the SCUBA-2 optical
response. The RMS of these fluctuations are then normalized to 0.002
pW so that they are comparable to the dynamic range of M17 itself. The
minimum is subtracted so that the signal is positive. Finally, half a
period of a (1+cosine)/2 function is used to roll-off the signal to
zero between radii of 300 and 400 arcsec.

The first row of Fig.~\ref{fig:m17_jk} shows the total signal image
averaging the maps made of each independent half of the data, for the
default configuration (inverse-variance weighting has been used). The
columns show reductions using 150, 300, and 600\,arcsec filter edges
in the reductions. The synthetic data are clearly seen as the circular
region S.E. of M17. As the filter scale is increased, the size of the
ripples increases accordingly. While larger structures do seem to
appear, negative bowls are a major problem without any other map
constraints.The second row of Fig.~\ref{fig:m17_jk} shows the
jackknife maps. The astronomical emission is almost perfectly removed,
except for a slight impression of M17 near the centre of the map that
is probably due to some combination of detector gain and pointing
drifts.
